---
title: "Synthetic comparison figures"
author: "Andrew Mertens"
date: "7/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)

library(tidyverse)
library(here)
library(knitr)

theme_ki <- function() {
  theme_bw() %+replace%
    theme(
      strip.background = element_blank(),
      #legend.position="none",
      plot.title = element_text(size = 16, face = "bold"),
      strip.text = element_text(size=14),
      axis.title = element_text(size=12),
      axis.text.y = element_text(size=10),
      axis.text.x = element_text(size=10, angle = 0, hjust = 0.5, vjust=.1)
    )
}

theme_set(theme_ki())

```


```{r, include="F"}
fig_dir="C:/Users/andre/Documents/HBGDki/ki-synthetic/figures/"
fig_dir="/home/andrew.mertens/ki-synthetic/figures/"
BV_dir="/home/andrew.mertens/ki-synthetic/"

pPAR <- readRDS(paste0(BV_dir,"/results/rf results/rf_Zpar_plot_objects.RDS"))
pATE <- readRDS(paste0(BV_dir, "/results/rf results/ate_diff_object.RDS"))
pPAR_unadj <- readRDS(paste0(BV_dir,"/results/rf results/rf_Zpar_unadj_plot_objects.RDS"))
pATE_unadj <- readRDS(paste0(BV_dir, "/results/rf results/ate_diff_object_unadj.RDS"))


load(paste0(BV_dir,"/figures/wasting/fig-comparisons.Rdata"))
WLZ_plot <- Z_plot
wast_plot <-prev_plot
wast_ci_plot <-ci_plot
wast_ci_africa_plot <-ci_plot_Africa
#sevwast_plot

load(paste0(BV_dir,"/figures/stunting/fig-comparisons.Rdata"))
LAZ_plot <- Z_plot
stunt_plot <- prev_plot_pooled
sevstunt_plot <- prev_plot_sev
stunt_ci_plot <- ci_plot
stunt_prev_cohort <- prev_plot


pwhz <- readRDS(file=paste0(fig_dir, "plot-objects/fig-WLZ-comp.RDS"))
phaz <- readRDS(file=paste0(fig_dir, "plot-objects/fig-LAZ-comp.RDS"))


```

## Dataset descriptions

The report compares estimates from 3 synthetic datasets with the raw KI values. The synthetic datasets are labeled:

  *  QI: Partially synthetic dataset with just quasi-identifiers synthesized
  *  BC: Partially synthetic dataset with quasi-identifiers and baseline characteristics synthesized, but not child age/anthropometry
  *  Full: Fully synthesized dataset using updated deep learning model. Each cohort is generated through a model either trained exclusively on that cohort, or on a group of sufficiently similar cohorts, depending on the number of individuals in the cohort.
  
### For the QI dataset, the following variables were synthesized:
QI_syn_cov <-  c("country", "arm", "sex",  "brthyr", "brthmon", "brthweek",  "W_mage", "mage", "W_mhtcm", "mhtcm", "W_mwtkg", "mwtkg",
"W_mbmi",  "mbmi", "W_meducyrs", "meducyrs", "single", "W_fage", "fage", "W_fhtcm", "fhtcm", "W_feducyrs", "feducyrs",
"hhwealth_quart", "dead")

### For the BC dataset, the following variables were synthesized:
BC_syn_cov <-  c( "country", "measurefreq", "arm", "sex", "W_gagebrth", "gagebrth", "vagbrth", "hdlvry", "brthyr", "brthmon", "brthweek",
"earlybf", "predexfd6", "W_parity", "parity", "W_mage", "mage", "W_mhtcm", "mhtcm", "W_mwtkg", "mwtkg", "W_mbmi",
"mbmi", "W_meducyrs", "meducyrs", "single", "W_fage", "fage", "W_fhtcm", "fhtcm", "W_feducyrs", "feducyrs",
"hhwealth_quart", "hfoodsec", "impsan", "safeh2o", "trth2o", "cleanck", "impfloor", "W_nrooms", "nrooms",  "W_nhh",
"nhh", "W_nchldlt5", "nchldlt5", "W_perdiar6", "perdiar6", "W_perdiar24", "perdiar24", "dead", "agedth")

  


## Descriptive epidemiology comparisons of Z-scores and age-specific wasting and stunting prevalences/incidences


Anthropometry estimates match exactly between the real data and the QI/BC datasets, but while mean Z-scores from the fully synthetic data match overall (and mostly match by age), the prevalences and incidences of wasting and stunting are lower because the standard deviation of Z-scores in the full synthetic data is lower than the real. 


```{r, echo=FALSE}

synfull <- readRDS(here("data/ki-synthetic-dataset.rds"))
  tab<- synfull %>% group_by(syntype) %>%
    summarize(`Mean HAZ`=round(mean(haz, na.rm=T),2), `Mean WHZ`=round(mean(whz, na.rm=T),2), `SD HAZ`=round(sd(haz, na.rm=T),2), `SD WHZ`=round(sd(whz, na.rm=T),2))
    
knitr::kable(tab)
  
```


### Mean Z-scores


```{r, echo=FALSE, fig.height = 6, fig.width = 8, fig.align = "center"}

LAZ_plot
WLZ_plot


```


<!-- # ```{r, echo=FALSE, fig.height = 6, fig.width = 8, fig.align = "center"} -->
<!-- #  -->
<!-- # phaz -->
<!-- # pwhz -->
<!-- #  -->
<!-- # ``` -->
<!-- #  -->
<!-- # __Note:__ `Recalculated` are Z-scores calculated using the growthstandard() R package from the synthetic height, weight, and age variables, versus the `Synthetic` Z-scores, which are the directly-synthesized Z-scores.  -->


### Stunting  prevalence

```{r, echo=FALSE, fig.height = 6, fig.width = 8, fig.align = "center"}

#Stunting
stunt_plot$plot




```

Note slight difference in stunting prevalence between real and QI/BC data. These should match exactly so I'm digging deeper to see if there is a slight different in code (most likely) or an actual difference in the underlying data affecting the prevalence estimates.

### Wasting prevalence

```{r, echo=FALSE, fig.height = 6, fig.width = 8, fig.align = "center"}


#Wasting
wast_plot$plot


```

### Severe stunting prevalence


```{r, echo=FALSE, fig.height = 6, fig.width = 8, fig.align = "center"}
#Stunting
sevstunt_plot$plot



```

### Severe  wasting prevalence


```{r, echo=FALSE, fig.height = 6, fig.width = 8, fig.align = "center"}

#Wasting
sevwast_plot$plot

```

### Stunting  cumulative incidence


```{r, echo=FALSE, fig.height = 6, fig.width = 8, fig.align = "center"}

#Stunting
stunt_ci_plot$plot


```


### Wasting cumulative incidence


```{r, echo=FALSE, fig.height = 6, fig.width = 8, fig.align = "center"}

wast_ci_plot$plot
```


### Example cohort-specific estimates of wasting cumulative incidenc eby age


```{r, echo=FALSE, fig.height = 6, fig.width = 8, fig.align = "center"}

wast_ci_africa_plot$plot

```

The fully synthesized data matches much more closely in some cohorts than others.


## Covariate-adjusted, SuperLearner-based estimates

Below are comparisons of the most challenging results to replicate with synthetic data: pooled population attributable risks of different baseline covariates on Z-scores at 24 months, estimated using targeted maximum likelihood estimation fit with SuperLearner ensemble machine learning models. 

### Comparison of pooled targeted learning estimates


```{r, echo=FALSE, fig.height = 8, fig.width = 8, fig.align = "center"}

pPAR[[1]] + theme(legend.position = "bottom")
pPAR[[2]] + theme(legend.position = "bottom")
```

The synthetic data population-attributable risks are generally lower than the real estimates.  The fully-synthetic data most closely matches the real-data estimates except for non-synthesized QI risk factors, though those have some small differences due to synthesized adjustment covariates. Also, the fully-synthesized estimates most closely mathc the real-data estimates for the strongest, most important risk factors. The fully synthesized data confidence intervals are generally higher than from the real data. We would have made similar inferences for many but not all of risk factors using the fully synthetic data, but would have concluded that some important risk factors (like father;s education and improved sanitation are not strongly associated with poor child growth).


### Comparison of difference in cohort-specific targeted learning estimates

```{r, echo=FALSE, fig.height = 8, fig.width = 8, fig.align = "center"}

pATE
```

The median difference between the real data estimates and the QI and full data is closer to 0 than from the BC data. The variance in the difference between real data and synthetic data estimates is larger for the fully synthesized data than the QI dataset.

## Unadjusted, linear regression estimates

### Comparison of pooled targeted learning estimates


```{r, echo=FALSE, fig.height = 8, fig.width = 8, fig.align = "center"}

pPAR_unadj[[1]]
pPAR_unadj[[2]]
```

Because these estimates are not adjusted for other covariates, the QI and real data estimates match exactly for non-synthesized risk factors, but differ for synthesized risk factors. How well each dataset specific risk factor matched the real-data estimates varies by risk factor. 

### Comparison of difference in cohort-specific unadjusted estimates



```{r, echo=FALSE, fig.height = 8, fig.width = 8, fig.align = "center"}

pATE_unadj
```

These comparisons don't include the QI risk factors that were not synthesized. The median estimate is slightly closer to the real data estimates when using the fully synthesized data, and the variance in the estimate differences are similar across the three different methods.


