---
title: "Synthetic comparison figures"
author: "Andrew Mertens"
date: "6/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)

library(tidyverse)
library(here)
library(knitr)

theme_ki <- function() {
  theme_bw() %+replace%
    theme(
      strip.background = element_blank(),
      #legend.position="none",
      plot.title = element_text(size = 16, face = "bold"),
      strip.text = element_text(size=14),
      axis.title = element_text(size=12),
      axis.text.y = element_text(size=10),
      axis.text.x = element_text(size=10, angle = 0, hjust = 0.5, vjust=.1)
    )
}

theme_set(theme_ki())

```


```{r, include="F"}
fig_dir="C:/Users/andre/Documents/HBGDki/ki-synthetic/figures/"

load(paste0(fig_dir, "cov-comparisons.Rdata"))


```

## Dataset descriptions

The report compares estimates from 3 synthetic datasets with the raw KI values. The synthetic datasets are labeled:

  *  QI: Partially synthetic dataset with just quasi-identifiers synthesized
  *  BC: Partially synthetic dataset with quasi-identifiers and baseline characteristics synthesized, but not child age/anthropometry
  *  Full: Fully synthesized dataset using updated deep learning model. Each cohort is generated through a model either trained exclusively on that cohort, or on a group of sufficiently similar cohorts, depending on the number of individuals in the cohort.
  


## Covariate comparisons

### Real versus QI


```{r, echo=FALSE}

summary(QI_comp)

```

### Real versus BC

```{r, echo=FALSE}

summary(BC_comp)

```

### Real versus Fully synthesized

```{r, echo=FALSE}

summary(FULL_comp)

```

