---
title: "Synthetic comparison figures"
author: "Andrew Mertens"
date: "6/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r, include="F"}
fig_dir="C:/Users/andre/Documents/HBGDki/ki-synthetic/figures/"

pPAR <- readRDS("C:/Users/andre/Documents/HBGDki/ki-synthetic/results/rf results/rf_Zpar_plot_objects.RDS")
pATE <- readRDS(paste0(here::here(), "/results/rf results/ate_diff_object.RDS"))


load("C:/Users/andre/Documents/HBGDki/ki-synthetic/figures/wasting/fig-comparisons.Rdata")
WLZ_plot <- Z_plot
wast_plot <-prev_plot
wast_ci_plot <-ci_plot
wast_ci_africa_plot <-ci_plot_Africa
#sevwast_plot

load("C:/Users/andre/Documents/HBGDki/ki-synthetic/figures/stunting/fig-comparisons.Rdata")
LAZ_plot <- Z_plot
stunt_plot <- prev_plot_pooled
sevstunt_plot <- prev_plot_sev
stunt_ci_plot <- ci_plot
stunt_prev_cohort <- prev_plot



pwhz <- readRDS(file=paste0(fig_dir, "plot-objects/fig-WLZ-comp.RDS"))
phaz <- readRDS(file=paste0(fig_dir, "plot-objects/fig-LAZ-comp.RDS"))


```


## Mean Z-scores


```{r, echo=FALSE, fig.height = 8, fig.width = 8, fig.align = "center"}

LAZ_plot
WLZ_plot


```


<!-- # ```{r, echo=FALSE, fig.height = 8, fig.width = 8, fig.align = "center"} -->
<!-- #  -->
<!-- # phaz -->
<!-- # pwhz -->
<!-- #  -->
<!-- # ``` -->
<!-- #  -->
<!-- # __Note:__ `Recalculated` are Z-scores calculated using the growthstandard() R package from the synthetic height, weight, and age variables, versus the `Synthetic` Z-scores, which are the directly-synthesized Z-scores.  -->


## Stunting  prevalence

```{r, echo=FALSE, fig.height = 8, fig.width = 8, fig.align = "center"}

#Stunting
stunt_plot$plot




```

## Wasting prevalence

```{r, echo=FALSE, fig.height = 8, fig.width = 8, fig.align = "center"}


#Wasting
wast_plot$plot


```

## Severe stunting prevalence


```{r, echo=FALSE, fig.height = 8, fig.width = 8, fig.align = "center"}
#Stunting
sevstunt_plot$plot



```

## Severe  wasting prevalence


```{r, echo=FALSE, fig.height = 8, fig.width = 8, fig.align = "center"}

#Wasting
sevwast_plot$plot

```

## Stunting  cumulative incidence


```{r, echo=FALSE, fig.height = 8, fig.width = 8, fig.align = "center"}

#Stunting
stunt_ci_plot$plot


```


## Wasting cumulative incidence


```{r, echo=FALSE, fig.height = 8, fig.width = 8, fig.align = "center"}



#Wasting
wast_ci_plot$plot
wast_ci_africa_plot$plot
```

## Comparison of pooled targeted learning estimates


```{r, echo=FALSE, fig.height = 8, fig.width = 8, fig.align = "center"}

pPAR[[1]]
pPAR[[2]]
```


## Comparison of pooled targeted learning estimates

Note "BC" estimates match the real-data estimates almost exactly and are not plotted

```{r, echo=FALSE, fig.height = 8, fig.width = 8, fig.align = "center"}

pATE
```


